### 2024-06-08 draft.qmd
20240608 - reorganize

In both [snake](#sec-draftStrategySnake) and [auction](#sec-draftStrategyAuction) draft formats, your goal is to draft the team whose weekly starting lineup scores the most points and thus the collection of players with the greatest [VORP](#sec-fantasyValueVORP).
However the draft strategies to achieve that differ between [snake](#sec-draftStrategySnake) versus [auction](#sec-draftStrategyAuction) drafts.

@@

For your starting lineup, it may make sense—especially with your earliest selections—when comparing two players with equivalent [VORP](#sec-fantasyValueVORP), to prioritize players with higher [consistency](#sec-evalHistoricalConsistency) and lower [uncertainty](#sec-fantasyValueUncertainty), because they may be considered "safer" with a higher floor.
However, when drafting your bench players, it make make more sense to prioritize high risk, high reward players with greater [uncertainty](#sec-fantasyValueUncertainty), because they may have a higher ceiling.
The Spurs in the National Basketball Association (NBA) were well-reputed for excelling in this draft strategy.
They frequently used their second-round picks to draft high-risk, high-reward players; sometimes, the secound round pick was a bust, but other times their second round picks including Manu Ginobili and Tony Parker greatly outperformed expectations and contributed to the team's strong success.

>>>>

In both [snake](#sec-draftStrategySnake) and [auction](#sec-draftStrategyAuction) draft formats, your goal is to draft the team whose weekly starting lineup scores the most points and thus the collection of players with the greatest [VORP](#sec-fantasyValueVORP).
For your starting lineup, it may make sense—especially with your earliest selections—when comparing two players with equivalent [VORP](#sec-fantasyValueVORP), to prioritize players with higher [consistency](#sec-evalHistoricalConsistency) and lower [uncertainty](#sec-fantasyValueUncertainty), because they may be considered "safer" with a higher floor.
However, when drafting your bench players, it make make more sense to prioritize high risk, high reward players with greater [uncertainty](#sec-fantasyValueUncertainty), because they may have a higher ceiling.
The Spurs in the National Basketball Association (NBA) were well-reputed for excelling in this draft strategy.
They frequently used their second-round picks to draft high-risk, high-reward players; sometimes, the secound round pick was a bust, but other times their second round picks including Manu Ginobili and Tony Parker greatly outperformed expectations and contributed to the team's strong success.

However, the draft strategies to achieve the "optimal lineup" differ between [snake](#sec-draftStrategySnake) versus [auction](#sec-draftStrategyAuction) drafts.

@@
